### 2015-01-18 src/methodology.Rnw
update

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement Deletion} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However,
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.

>>>>

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement deletion emulation} \label{subsec:stmtdel}

The statement deletion based operator selection was based on the work by
Deng et al.~\cite{deng2013empirical}. The operations on single
statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
\Pitri~for simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.

Note that we are not attempting to evaluate statement deletion mutation
directly here. Rather, we have chosen a set of operators that could be
involved in deletion of statements, and have used that as an operator
selection criteria. This means that in order to translate the results
from our experiment back to original statement deletion operator, we need
to rely on some assumptions. They are, 1) Coupling effect: If a test is
able to kill a mutant in this set, then it should kill it even when it
is in combination with other mutants of this set (resulting in deletion
of deletion of the statement in question). Note that there is a
possibility for statement deletion to be less effective than our
experiment, that is, for actual deleted statements to be detected more
often than individual mutants are detected. However, this does not adversely
affect our final conclusions.

Finally, while the utility measures and the effectiveness for deletion based
operators should hold when translating to true statement deletion, the mutation
share reported is based on the independent mutants, and should not be taken
as the mutation share of true statement deletion.

% Finally, to get an accurate estimation
% of the effect of true statement deletion, we grouped the mutants by
% line, and considered each line a single virtual mutant (that is, the total
% number of mutants is equal to the total number of lines). Further,
% killing any mutant from a line resulted in marking the virtual mutant
% for that line as killed. This gave us the mutation score for the
% virtual statement deletion operator.  We note that the approximation
% of simple statement deletion, especially when arithmetic operators are
% involved, is not complete. However,
% the number of mutants produced by \pitm operator is very small. We
% also note that our approximation does not account for the increase in
% ease of detection when multiple mutations are combined together due to
% the coupling effect. This also means that not all the lines may be
% mutated ,since there may be no applicable operators. However, given
% the constraints of a bytecode based mutation system, we believe that
% our procedure is reasonable.
% An interesting point is that using this

%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.

### 2015-01-18 src/tables.Rnw
update

\begin{table*}[!ht]
%\caption*{Selective}
<<results='asis'>>=
eff <- function(v) {
  v$strategy.effectiveness <- v$strategy.effectiveness - v$baseline.effectiveness
  return(v)
}
tbl.place <- function(xtb) {
  align(xtb) <- "p{0.1\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}"
  return(xtb)
}
print(tbl.place(xtable(eff(s.selective.db), caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection strategy}
\label{tbl:selective}
\end{table*}

>>>>

\begin{table*}[!ht]
%\caption*{Selective}
<<results='asis'>>=
eff <- function(v) {
  v$strategy.effectiveness <- v$strategy.effectiveness - v$baseline.effectiveness
  return(v)
}
tbl.place <- function(xtb) {
  align(xtb) <- "p{0.1\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}"
  return(xtb)
}
# s.selective.db['sdl','mutation.share'] <- -1 #paste(s.opsample.db['sdl','mutation.share'],'*')
print(tbl.place(xtable(eff(s.selective.db), caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection strategy}
\label{tbl:selective}
\end{table*}
